Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
Introduction nudge more contributions

Whilst there is a vast literature on validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on stability %, working typically on continuous domains
\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
Reachability tools are
also used when discretizing the state-space for verification and
parametric synthesis~\cite{cimatti2013parameter}.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller and the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this particular work we focus
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic) %\addtodo{[clarify next] with known configurations} 
and perform %parametric 
synthesis of safe digital controllers.

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we employ abstract acceleration
to accelerate the dynamics forward instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

\textit{Contributions}. We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
safety properties over the state space. In an alternative approach, we use a verification engine based 
on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
the transition system necessarily for the first approach. In both approaches, we project
the maximum effect of the noise over an unbounded time and uses it as a buffer region 
for the safety specification.

>>>>

Although there is a vast literature on validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on stability %, working typically on continuous domains
\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
Reachability tools are
also used when discretizing the state-space for verification and
parametric synthesis~\cite{cimatti2013parameter}.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller and the hybrid elements that relate them.  
Due to the complexity of such systems, in this particular work we focus
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic) and perform synthesis of safe digital controllers.

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system whilst remaining safe given a 
pre-selected time horizon; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we employ abstract acceleration
to accelerate the dynamics forward instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

\textit{Contributions}. We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
safety properties over the state space. 
In an alternative approach, we use a verification engine based 
on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
in order to make it less conservative, and develop a CEGIS feedback based on abstraction refinement to
increase the speed of the synthesis algorithm.
In both approaches, we project the maximum effect of the noise over an unbounded time and uses it as a buffer region 
for the safety specification.
